manuscript_modelling_and_plots_takeovers

### 2024-11-22 manuscript_and_modelling_plots_takeovers.Rmd
analysis code and extra plots

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig4.tiff"), plot = fig4, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
```

@@

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig8.tiff"), plot = fig8, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
```

@@

ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig12.tiff"), plot = fig12, width = 16, height = 18, units = 'cm', dpi = 300, type = 'cairo')
```

>>>>

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig4.tiff"), plot = fig4, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Figures/Fig4.png"), plot = fig4, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
```

@@

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig8.tiff"), plot = fig8, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')

# plot saving
ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig8.png"), plot = fig8, width = 16, height = 12, units = 'cm', dpi = 300, type = 'cairo')
```

@@

ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig12.tiff"), plot = fig12, width = 16, height = 18, units = 'cm', dpi = 300, type = 'cairo')

ggsave(here::here("takeover_performance_cogload_time_budget/Figures/fig12.png"), plot = fig12, width = 16, height = 18, units = 'cm', dpi = 300, type = 'cairo')
```
